Streaming Slot-Value Extraction for Wikipedia Entities at Web-Scale

### 2013-11-05 paper/flairs27/content/results.tex
Some table shortenning

\begin{table*}
\caption{Document Chunks Distribution }
\centering
\label{table:documentsDist}

\begin{tabular}{|c|l|}
\hline 
\textbf{\# of Documents} & \textbf{Document Type}\\ 
\hline 
10988 & 	arxiv (full text, abstracts in StreamItem.other\_content) \\ \hline
34887 & CLASSIFIED (spinn3r)  \\ \hline
77674 & FORUM (spinn3r)  \\ \hline
12947 & linking (reprocessed from kba-stream-corpus-2012, same stream\_id)  \\ \hline
141936 & MAINSTREAM\_NEWS (spinn3r)  \\ \hline
4137 & MEMETRACKER (spinn3r)  \\ \hline
280629 & news (reprocessed from kba-stream-corpus-2012, same stream\_id)  \\ \hline
6347 &  REVIEW (spinn3r) \\ \hline
688848 & 	 social (reprocessed from kba-stream-corpus-2012 plus extension, same stream\_id)  \\ \hline
740987 & WEBLOG (spinn3r)  \\ \hline

\hline 
\end{tabular} 
\end{table*}

@@

\begin{table}
\caption{Benchmark Server Specifications }
\centering
\label{table:serverspec}
\begin{tabular}{| c | p{5cm} |}
\hline 
\textbf{Spec} & \textbf{Details} \\ \hline
Model & Dell xxx 32 cores \\ \hline 
OS & CentOS release 6.4 Final \\ \hline 
Software Stack & GCC version 4.4.7, Java 1.7.0\_25, Scala 2.9.2, SBT 0.12.3 \\ \hline 
 RAM & 64GB\\ \hline 
 Drives & 2x2.7TB disks, 6Gbps, 7200RPM\\ \hline 
\end{tabular} 
\end{table}

\begin{table}
\caption{SSF Performance Measure on \textit{initial\_submission} }
\centering
\label{table:initialresult}

@@

\begin{table*}    
\caption{Recall Measure on \textit{submission\_infer}: Generic slot names like affiliate had the most recall, compared to less popular slot names e.g. DateOfDeath}
\centering
\label{table:finalresultrecall}
\begin{tabular}{|l|p{3.5cm}|p{4cm}|}
\hline 
 \textbf{Slot Name} & \textbf{Total instances of slot value found} & \textbf{\# of entities covered by slot value} \\ 
\hline 
Affiliate & 108598 & 80 \\ \hline 
AssociateOf & 25278 & 106 \\ \hline 
AwardsWon & 38 & 14 \\ \hline 
CauseOfDeath & 0 & 0 \\ \hline 
Contact\_Meet\_Entity & 191 & 8 \\ \hline 
Contact\_Meet\_PlaceTime & 5974 & 109 \\ \hline 
DateOfDeath & 87 & 14 \\ \hline 
EmployeeOf & 75 & 16 \\ \hline 
FoundedBy & 326 & 30 \\ \hline 
FounderOf & 302 &  29 \\ \hline 
Titles & 26823 & 118 \\ \hline 
TopMembers & 314 & 26 \\ \hline

\end{tabular} 
\end{table*}

\begin{table*}
\caption{SSF Accuracy Measure on \textit{submission\_infer}: Accuracy of AffiliateOf was the best and Affiliate applied poorly due to ambiguity of being an affiliate of somebody/something}
\centering
\label{table:finalresultaccuracy}
\begin{tabular}{|l|c|c|c|}
\hline 
 \textbf{Slot Name}  & \textbf{Correct} & \textbf{Incorrect Entity name} & \textbf{Incorrect Value} \\ 
\hline 
Affiliate & 1\% & 95\% & 5\% \\ \hline 
AssociateOf & 63.6\% & 9.1\% & 27.3\%  \\ \hline 
AwardsWon & 10\% & 10\% & 80\%  \\ \hline 
CauseOfDeath & 0\% & 0\% & 0\%  \\ \hline 
Contact\_Meet\_Entity & 21\% & 42\% & 37\%  \\ \hline 
Contact\_Meet\_PlaceTime & 5\% & 20\% & 85\%  \\ \hline 
DateOfDeath & 29.6\% & 71\% & 25\%  \\ \hline 
EmployeeOf & 5\% & 30\% & 65\%  \\ \hline 
FoundedBy & 62\% & 17\% & 21\%  \\ \hline 
FounderOf & 50\% & 0\% & 50\%  \\ \hline 
Titles & 55\% & 0\% & 45\%  \\ \hline 
TopMembers & 33\% & 17\% & 50\%  \\ \hline

\end{tabular} 
\end{table*}

>>>>

\begin{table}
\caption{Document Chunks Distribution }
\centering
\label{table:documentsDist}

\begin{tabular}{|c|l|}
\hline 
\textbf{\# of Documents} & \textbf{Document Type}\\ 
\hline 
10988 & 	arxiv  \\ \hline
34887 & Classified \\ \hline
77674 & Forum  \\ \hline
12947 & Linking  \\ \hline
141936 & Mainstream News  \\ \hline
4137 & Memetracker \\ \hline
280629 & News \\ \hline
6347 &  Review \\ \hline
688848 & 	 Social  \\ \hline
740987 & Weblog \\ \hline

\hline 
\end{tabular} 
\end{table}

@@

\begin{table}
\caption{Benchmark Server Specifications }
\centering
\label{table:serverspec}
\begin{tabular}{| c | p{4.8cm} |}
\hline 
\textbf{Spec} & \textbf{Details} \\ \hline
Model & Dell xxx 32 cores \\ \hline 
OS & CentOS release 6.4 Final \\ \hline 
Software Stack & GCC version 4.4.7, Java 1.7.0\_25, Scala 2.9.2, SBT 0.12.3 \\ \hline 
 RAM & 64GB\\ \hline 
 Drives & 2x2.7TB disks, 6Gbps, 7200RPM\\ \hline 
\end{tabular} 
\end{table}

\begin{table}[htp]
\caption{SSF Performance Measure on \textit{initial\_submission} }
\centering
\label{table:initialresult}

@@

\begin{table}[h]

\caption{Recall Measure on \textit{submission\_infer}: Generic slot names like affiliate had the most recall, compared to less popular slot names e.g. DateOfDeath}
\centering
\label{table:finalresultrecall}
\begin{tabular}{|l|c|c|}
\hline 
 \textbf{Slot Name} & \textbf{Instances Found} & \textbf{Entity Coverage} \\ 
\hline 
Affiliate & 108598 & 80 \\ \hline 
AssociateOf & 25278 & 106 \\ \hline 
AwardsWon & 38 & 14 \\ \hline 
CauseOfDeath & 0 & 0 \\ \hline 
{\tiny Contact\_Meet\_Entity} & 191 & 8 \\ \hline 
{\tiny Contact\_Meet\_PlaceTime} & 5974 & 109 \\ \hline 
DateOfDeath & 87 & 14 \\ \hline 
EmployeeOf & 75 & 16 \\ \hline 
FoundedBy & 326 & 30 \\ \hline 
FounderOf & 302 &  29 \\ \hline 
Titles & 26823 & 118 \\ \hline 
TopMembers & 314 & 26 \\ \hline

\end{tabular}

\caption{SSF Accuracy Measure on \textit{submission\_infer}: Accuracy of AffiliateOf was the best and Affiliate applied poorly due to ambiguity of being an affiliate of somebody/something}
\centering
\label{table:finalresultaccuracy}
\begin{tabular}{|l|c|c|p{13mm}|}
\hline 
 \textbf{Slot Name}  & \textbf{Correct} & \textbf{Wrong Entity} & {\small \textbf{Incorrect Value}} \\ 
\hline 
Affiliate & 1\% & 95\% & 5\% \\ \hline 
AssociateOf & 63.6\% & 9.1\% & 27.3\%  \\ \hline 
AwardsWon & 10\% & 10\% & 80\%  \\ \hline 
CauseOfDeath & 0\% & 0\% & 0\%  \\ \hline 
{\tiny Contact\_Meet\_Entity} & 21\% & 42\% & 37\%  \\ \hline 
{\tiny Contact\_Meet\_PlaceTime} & 5\% & 20\% & 85\%  \\ \hline 
DateOfDeath & 29.6\% & 71\% & 25\%  \\ \hline 
EmployeeOf & 5\% & 30\% & 65\%  \\ \hline 
FoundedBy & 62\% & 17\% & 21\%  \\ \hline 
FounderOf & 50\% & 0\% & 50\%  \\ \hline 
Titles & 55\% & 0\% & 45\%  \\ \hline 
TopMembers & 33\% & 17\% & 50\%  \\ \hline

\end{tabular} 
\end{table}
